---
title: GitLab Advisory Database Stats
output:
  html_document:
    toc: false
    theme: united
---

### Adivsory distribution

The pie chart below illustrates the advisory distribution for the package types we support by providing their total number and percentages.

```{r echo=FALSE}
source('compute_charts.R')
package_type_distro('../data/mttm.csv')
```


### Number of CVEs

The pie chart below illustrates how many advisories in the database are originating from CVE vs Non-CVE sources.

```{r echo=FALSE}
source('compute_charts.R')
cve_distro('../data/mttm.csv')
```


### Number of merged CVEs

The barchart below depicts the number of advisories (CVEs only) that have been merged during the last couple of months starting from May 2019 where the initial data was imported to gemnasium-db.

```{r echo=FALSE}
source('compute_charts.R')
merged_advisories('../data/mttm.csv')
```


### Throughput

Throughput illustrates how efficient we are in adding new advisories to gemnasium-db. With more automation we should be able to increase the throughput.
The plot below shows how the throughput developed over the last couple of month. For every month throughput is computed with: $\frac{\text{#Advisories}}{\text{day}}$.

```{r echo=FALSE}
source('compute_charts.R')
throughput('../data/mttm.csv')
```


### Coverage 

Coverage indicates how many advisories in the NVD have been identified as relevant in the context of dependency scanning. The barchart below shows how many CVEs (in %) were translated into advisories because they are related to a package. The X-axis depicts the year of the NVD data feed wheras the Y-asis depicts percentage of extracted CVEs.

```{r echo=FALSE}
source('compute_charts.R')
coverage('../data/mttm.csv', '../data/nvd.csv')
```

